Lifting CDCL to Numerical Domains

### 2016-10-11 example.tex
figure added

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & Control-Flow Graph & Decision Procedure Statistics\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
 int x,result1=0,result2=0;
 assume(x>=1 && x<= N);
 result1 = 2*x; 
 int state = 1;
 int y=x;
 while(state!=0) {
  switch(state) {
   case 0: state = 1; break;
   case 1: state = 2; break;
   case 2: x--; y++;
   if(x == 0) state = 0;
   else state = 1; break;
  } 
 }
 result2 = y;
 assert(result1 == result2);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{lstlisting}[mathescape=true,language=C]
                 SAT solver  ACDCL 
                 ----------- ----- 
restarts           1          0
conflicts  :       5          2
decisions  :       36         2 
propagations :     1365       240  
conflict literals  65         4   
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program, CFG and statistics for decision procedure}
\label{example}
\end{figure}
Let us consider a simple program in Figure~\ref{example} that checks 
the equivalence of a state-machine based interger multiplication against  
a specification that uses multiplication operator (*).  The assertion 
simply compares the result of two multiplication for an input $x$.  To 
avoid overflow error, we assume $x$ has an upper bound $N$.  The 
control flow graph is shown in the middle column of Figure~\ref{example}.

@@

>>>>

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & Control-Flow Graph & Decision Procedure Statistics\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
 int x,result1=0,result2=0;
 assume(x>=1 && x<= N);
 result1 = 2*x; 
 int state = 1;
 int y=x;
 while(state!=0) {
  switch(state) {
   case 0: state = 1; break;
   case 1: state = 2; break;
   case 2: x--; y++;
   if(x == 0) state = 0;
   else state = 1; break;
  } 
 }
 result2 = y;
 assert(result1 == result2);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{acdl_run.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, CFG and statistics for decision procedure}
\label{example}
\end{figure}
Let us consider a simple program in Figure~\ref{example} that checks 
the equivalence of a state-machine based interger multiplication against  
a specification that uses multiplication operator (*).  The assertion 
simply compares the result of two multiplication for an input $x$.  To 
avoid overflow error, we assume $x$ has an upper bound $N$.  The 
control flow graph is shown in the middle column of Figure~\ref{example}.

@@

\Omit{
\begin{tabular}{l|l|l|l|l|l}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\
SAT & 1 & 1365 & 5 & 65 & 1 \\
ACDCL & 1 & 23 & 1 & 1 & 0 \\
\hline
\end{tabular}
%\caption{Solver-statistics}
\label{solver}
\end{figure}
}
\begin{lstlisting}[mathescape=true,language=C]

                 SAT solver  ACDCL 
                 ----------- ----- 
restarts           1          0
conflicts  :       5          2
decisions  :       36         2 
propagations :     1365       240  
conflict literals  65         4   
\end{lstlisting}
